SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-10 docs/questioning.tex
add detection locus

>>>>

Detection mechanisms vary on the location where they detect an attack.
There are five different loci where an attack can be caught, as seen
in Figure~\ref{fig:attacks}:
\begin{itemize}
\item At the user's browser (Locus X).
\item En route from the server to the user's browser (Locus Y).
\item Embedded in a query, but before it reaches the server's database
  (Locus Z).
\item After the malicious code has been executed on the server's
  database (Locus $\Omega$).
\end{itemize}
